Preprocessing

### 2017-07-20 imputation.Rmd
review mike 1

NCORES <- parallel::detectCores() / 2
```

@@

```{r}
system.time(
  test <- snp_fastImpute(GNA, infos.chr = popres$map$chromosome, ncores = NCORES)
) # Latest timings: 42 / 48 minutes
```

@@

# Plot the estimation of the errors of imputation
data_frame(col = indNA[, 2], error = XNA[indNA] != X[indNA]) %>%
  group_by(col) %>%
  summarise(nb_err = sum(error)) %>%
  mutate(nb_err_est = (test$pError * test$pNA * n)[col]) %>%
  ggplot() %>%
  bigstatsr:::MY_THEME(coeff = 1.8) + 
  geom_abline(slope = 1, intercept = 0, col = "red") + 
  geom_point(aes(nb_err, nb_err_est), alpha = 0.4) +
  labs(x = "Number of errors", y = "Estimated number of errors")

@@

```{r}
system.time(
  bedfile2 <- snp_beagleImpute(beagle.path = "../../beagle.21Jan17.6cc.jar",
                               plink.path = "../plink_linux_x86_64/plink",
                               bedfile.in = "backingfiles/tmp.bed",
                               memory.max = 30,
                               ncores = NCORES)
) # 14.6 / 14.2 hours
```

>>>>

NCORES <- parallel::detectCores() / 2
PLINK <- "../plink_linux_x86_64/plink"
BEAGLE <- "../../beagle.21Jan17.6cc.jar"
```

@@

```{r}
system.time(
  infos <- snp_fastImpute(GNA, infos.chr = popres$map$chromosome, ncores = NCORES)
) # Latest timings: 42 / 48 minutes
```

@@

# Plot the estimation of the errors of imputation
data_frame(col = indNA[, 2], error = XNA[indNA] != X[indNA]) %>%
  group_by(col) %>%
  summarise(nb_err = sum(error)) %>%
  mutate(nb_err_est = (infos$pError * infos$pNA * n)[col]) %>%
  ggplot() %>%
  bigstatsr:::MY_THEME(coeff = 2) + 
  geom_abline(slope = 1, intercept = 0, col = "red") + 
  geom_point(aes(nb_err, nb_err_est), alpha = 0.4) +
  labs(x = "Number of errors", y = "Estimated number of errors")

@@

```{r}
system.time(
  bedfile2 <- snp_beagleImpute(beagle.path = BEAGLE,
                               plink.path = PLINK,
                               bedfile.in = "backingfiles/tmp.bed",
                               memory.max = 30,
                               ncores = NCORES)
) # 14.6 / 14.2 hours
```

### 2017-07-20 preprocessing.Rmd
review mike 1

```{r}

```

>>>>

```{r}
# Fast imputation
system.time(
  infos <- snp_fastImpute(G, celiac$map$chromosome, ncores = NCORES)
)
```

```{r}
plot(subset(infos, pNA > 0.001), pch = 19, cex = 0.5)
pvals <- c(0.01, 0.005, 0.002, 0.001); colvals <- 2:5
idc <- lapply(seq_along(pvals), function(i) {
  curve(pvals[i] / x, from = 0, lwd = 2, 
        col = colvals[i], add = TRUE)
})
legend("topright", legend = pvals, title = "p(NA & Error)",
       col = colvals, lty = 1, lwd = 2)
```

```{r}
big_counts(G, ind.col = 1:10)
```

```{r}
{{G@code <- bigsnpr:::CODE_IMPUTE_PRED}}
big_counts(G, ind.col = 1:10)
```
